---
title: "ExpediaProject"
author: "Group6"
date: "12/2/2018"
output: html_document
---
#preprocessing loading libraries and data cleaning

@. load naive bayes library
```{r setup, include=TRUE}
library(ggplot2)
library(dplyr)
library(naivebayes)
?naive_bayes
```
@. read all the original data 
```{r}
clean_data = read.csv(file = "all_data5.csv")
summary(clean_data)
```
@. remove the attributes "user_location_country", "hotel_continent"
```{r}
clean_data = subset(clean_data, select = -c(user_location_country, hotel_continent))
```
@. change all the data which is numerical before to categorical 
```{r}
for (i in 1:22) {
  clean_data[,i] = as.factor(clean_data[,i])
}
clean_data$hotel_cluster = as.factor(clean_data$hotel_cluster)
```
@. select the train data and the test data, training data is sampled 70% of all original data.
```{r}
set.seed(1)
train_id = sample(nrow(clean_data), nrow(clean_data)*0.7)
train_data = clean_data[train_id,]
test_data = clean_data[-train_id,]
test_data_y = test_data$hotel_cluster
```
@. make sure the label is categorical, so that the bayes algorithm can work properlly
```{r}
class(test_data$hotel_cluster)
```

#Build model

@. train the naive bayes model
```{r}
model = naive_bayes(hotel_cluster ~ ., data = train_data, laplace = 1)
```
@. use bayes model to predict the probability of hotel culster for each instance 
```{r}
predict_test_data_prob = predict(model, test_data, type = "prob")
```
@. create 10 columns to store the 10 hignest probability from naive bayes model for each instance
```{r}
test_data$pred1 = -1
test_data$pred2 = -1
test_data$pred3 = -1
test_data$pred4 = -1
test_data$pred5 = -1
test_data$pred6 = -1
test_data$pred7 = -1
test_data$pred8 = -1
test_data$pred9 = -1
test_data$pred10 = -1
test_data$outcome = FALSE
```
@. for each instance, inply hte model and store 10 hignest probability
from naive bayes model for each instance, and if one of the 19 finals 
outcomes matches the labal ,it means success.
```{r}
for (i in 1:10) {
  for (j in 1: nrow(predict_test_data_prob)) {
    temp = order(predict_test_data_prob[j,], decreasing = T)
    test_data[j, 22+i] = temp[i] -1
    if(test_data[j, 22+i] == test_data[j, "hotel_cluster"]){
      test_data[j, "outcome"] = TRUE
    }
  }
}
```

#Generate Final Result
@. check outcome
```{r}
summary(test_data$outcome)
```
@. the final accuracy is 0.6032636 for the 4th(final) version naive bayes model#10  
```{r}
34751/57605
```
@. The final accuracy for Naive Bayes Model is 0.6032636